Paper_analyses

### 2021-08-04 Paper_Analyses_subj_obje_arousal.Rmd
another paranoid check on valence arousal scaling
did an additional set of checks to see whether arousal was captured as an absolute of valence, and it doesn't map too well,  which suggests that our scale is picking something up that is not just magnitude of valence

```{r Scrap this}

@@

tmp.df4_full_stim_downs_jun2021_60bins%>%
  group_by(stimIAPS, ssid,ground_valence_2)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(stimIAPS, abs(arousal), color = ground_valence_2))+
  # geom_point()+
  stat_summary(funy = mean, geom = 'pointrange')

# Plot just positive
tmp.df4_full_stim_downs_jun2021_60bins %>%
  subset(ground_valence_2 == "positive")%>%
  group_by(stimDescription,ground_valence_2)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(stimDescription, arousal))+
  # geom_point()+
  stat_summary(funy = mean, geom = 'pointrange', color = "blue")+
   stat_summary(aes( y = ArousalMean), funy = mean, geom = 'pointrange', color = "red")+
  theme(axis.text.x = element_text(angle = 60))

@@

@@

# does absolute arousal correlate with other variables of interest
tmp.df4_full_stim_downs_jun2021_60bins$abs_arousal<- abs(tmp.df4_full_stim_downs_jun2021_60bins$arousal)

>>>>

check baselining onto specific valences
```{r Scrap this}

@@

absolutetest<- tmp.df4_full_stim_downs_jun2021_60bins%>%
  group_by(stimDescription,ground_valence_2)%>%
  # summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  mutate(arousal_abs = abs(arousal), valence_abs = abs(valence))%>%

  summarise_at(c("arousal", "ArousalMean", "ValenceMean","arousal_abs", "valence", "valence_abs", "arousal_abs_on_pos"), mean, na.rm = TRUE)

absolutetest %>%
  ggplot(aes(ValenceMean,arousal_abs))+
  geom_point()+
  geom_text(aes(label = stimDescription))

absolutetest %>%
  ggplot(aes(ArousalMean,arousal_abs))+
  geom_point()+
  geom_text(aes(label = stimDescription))

# he U shape relationship seems to hold dependign on whether arousal is absolute - converting actovation to absolute

# absolute arousal don't correlate with iaps arousal
# we we taking valence absolute as intensity
absolutetest %>%
  ggplot(aes(ValenceMean,valence_abs))+
  geom_point()+
  geom_text(aes(label = stimDescription))

# arousal vs absolute valence
absolutetest %>%
  ggplot(aes(ArousalMean,valence_abs))+
  geom_point()+
  geom_text(aes(label = stimDescription))+
  geom_smooth(method = 'lm', se = F)+
  ggpubr::stat_cor()
# it seems like arousal in our case is picking something that is not just intemnsity of vaence, as it correlates better with arousal Mean

absolutetest %>%
  ggplot(aes(valence,valence_abs))+
  geom_point()+
  geom_text(aes(label = stimDescription))+
  geom_smooth(method = 'lm', se = F)+
  ggpubr::stat_cor()

# try and compute correlation using valencabs(

tmp.df4_full_stim_downs_jun2021_60bins%>%
  subset(!is.na(ground_valence_2))%>%
  group_by(ssid, stimIAPS,ground_valence_2)%>%

  mutate(arousal_abs = abs(arousal), valence_abs = abs(valence))%>%
  group_by(ssid, ground_valence_2)%>%
  mutate(cortest = cor(valence_abs, pup_basCor, use = "complete"))%>%

  # summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  # summarise_at(c("arousal", "ArousalMean","ValenceMean", "arousal_abs", "valence", "valence_abs", "arousal_abs_on_pos"), mean, na.rm = TRUE) %>%

  ggplot(aes(ground_valence_2, cortest, color = ground_valence_2))+
  # geom_point()+
  stat_summary(funy = mean, geom = 'pointrange')
    theme(axis.text.x = element_text(angle = 60))

just positive check
```{r}
# Plot just positive
tmp.df4_full_stim_downs_jun2021_60bins %>%
  subset(ground_valence_2 == "positive")%>%
  group_by(stimDescription,ground_valence_2)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(stimDescription, arousal))+
  # geom_point()+
  stat_summary(funy = mean, geom = 'pointrange', color = "blue")+
   stat_summary(aes( y = ArousalMean), funy = mean, geom = 'pointrange', color = "red")+
  theme(axis.text.x = element_text(angle = 60))

@@

  tmp.df4_full_stim_downs_jun2021_60bins %>%
  subset(ground_valence_2 != "negative")%>%
  group_by(stimDescription,ground_valence_2)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(stimDescription, abs(arousal), color = ground_valence_2))+
  # geom_point()+
  stat_summary(funy = mean, geom = 'pointrange')+
   # stat_summary(aes( y = ArousalMean), funy = mean, geom = 'pointrange')+
  theme(axis.text.x = element_text(angle = 60))

  tmp.df4_full_stim_downs_jun2021_60bins$arousal_abs_on_pos<- if_else(tmp.df4_full_stim_downs_jun2021_60bins$ground_valence_2!= "negative", abs(tmp.df4_full_stim_downs_jun2021_60bins$arousal), tmp.df4_full_stim_downs_jun2021_60bins$arousal)

    tmp.df4_full_stim_downs_jun2021_60bins %>%
  # subset(ground_valence_2 != "negative")%>%
  group_by(stimDescription,ground_valence_2)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(ground_valence_2, arousal_abs_on_pos, color = ground_valence_2))+
  geom_point()+
  stat_summary(funy = mean, geom = 'pointrange')+
   # stat_summary(aes( y = ArousalMean), funy = mean, geom = 'pointrange')+
  theme(axis.text.x = element_text(angle = 60))

        tmp.df4_full_stim_downs_jun2021_60bins %>%
  # subset(ground_valence_2 != "negative")%>%
  group_by(stimDescription,ground_valence_2)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(ground_valence_2, abs(arousal), color = ground_valence_2))+
  # geom_point()+
  stat_summary(funy = mean, geom = 'pointrange')+
   # stat_summary(aes( y = ArousalMean), funy = mean, geom = 'pointrange')+
  theme(axis.text.x = element_text(angle = 60))

erotica check
```{r}
# if we removed the erotic ones would we have positive tracking arousal better?

@@

```{r}
# does absolute arousal correlate with other variables of interest
tmp.df4_full_stim_downs_jun2021_60bins$abs_arousal<- abs(tmp.df4_full_stim_downs_jun2021_60bins$arousal)
